---
output: github_document
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/AnthonyEbert/EasyMMD/workflows/R-CMD-check/badge.svg)](https://github.com/AnthonyEbert/EasyMMD/actions)
[![codecov](https://codecov.io/gh/AnthonyEbert/EasyMMD/branch/master/graph/badge.svg)](https://codecov.io/gh/AnthonyEbert/EasyMMD)
<!-- badges: end -->


<!-- README.md is generated from README.Rmd. Please edit that file -->

# EasyMMD

Gretton et al. (2007) introduced Maximum Mean Discrepancy (MMD). EasyMMD in an R package which provides a simple (hopefully!) and computationally efficient way to compute the MMD between two datasets.   

## Installation

You can install EasyMMD from github with:

```{r gh-installation, eval = FALSE}
devtools::install_github("AnthonyEbert/EasyMMD")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(EasyMMD)

n <- 1e3
x <- rnorm(n)
y <- rnorm(n, 5)


MMD(y,x)

# For faster computation, precompute part of the MMD for the observed data y

y_kmmd <- kmmd(y)

MMD(y,x, y_kmmd)

microbenchmark::microbenchmark(MMD(y,x), MMD(y,x, y_kmmd), times = 10)
```

## References

Gretton, A., Borgwardt, K. M., Rasch, M., Schölkopf, B., & Smola, A. J. (2007). A kernel method for the two-sample-problem. In Advances in neural information processing systems (pp. 513-520).
